---
title: "Manually Load pixarfilms Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Manually Load pixarfilms Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

This vignette here demonstrates how to manually load data without using the
{pixarfilms} package if you wish to explore and analyze this data elsewhere.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Loading within R

If for some reason, you don't wish to install the package officially, you can
also access the data by reading the data directly from GitHub using {readr}.

```{r}
library(readr)

pixar_films <- read_csv("https://raw.githubusercontent.com/erictleung/pixarfilms/main/data-raw/pixar_films.csv")
```


## Loading within Python and pandas

Similarly, you can read the data directly

```{python, eval=FALSE}
import pandas as pd

pixar_films = pd.read_csv("https://raw.githubusercontent.com/erictleung/pixarfilms/main/data-raw/pixar_films.csv")
```


## Data links

Here are the URL links you can use using the above methods.

```
https://raw.githubusercontent.com/erictleung/pixarfilms/main/data-raw/academy.csv
https://raw.githubusercontent.com/erictleung/pixarfilms/main/data-raw/box_office.csv
https://raw.githubusercontent.com/erictleung/pixarfilms/main/data-raw/genres.csv
https://raw.githubusercontent.com/erictleung/pixarfilms/main/data-raw/pixar_films.csv
https://raw.githubusercontent.com/erictleung/pixarfilms/main/data-raw/pixar_people.csv
https://raw.githubusercontent.com/erictleung/pixarfilms/main/data-raw/public_response.csv
```
