---
title: "Pixar Film Ratings"
description: |
  Explore the variation in box office ratings of the films.
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Pixar Film Ratings}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

This vignette is to recreate an analysis on Pixar ratings that can be found
[here](https://pierrecom.github.io/Pixars%20Movies.html).


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Setup

```{r setup, warning=FALSE}
library(pixarfilms)
library(dplyr)
library(tidyr)
library(forcats)
library(ggplot2)
library(stringr)
library(irr)
```


## Data wrangling

Before we can visualize our data, let's wrangle our data to help us visualize it
later on.

```{r}
df <-
  public_response|>
  select(-cinema_score, -ends_with("counts"), -ends_with("votes"), -letterboxd_num_fans) |>
  mutate(
    imdb_score = imdb_score * 10,
    letterboxd_rating = letterboxd_rating * 20
  ) |>
  mutate(film = fct_inorder(film)) |>
  pivot_longer(cols = -film,
               names_to = "ratings",
               values_to = "value") |>
  mutate(ratings = case_when(
    ratings == "imdb_score" ~ "IMDb (Scaled)",
    ratings == "rotten_tomatoes_score" ~ "Rotten Tomatoes",
    ratings == "metacritic_score" ~ "Metacritic",
    ratings == "rotten_tomatoes_score_top_critics" ~ "Rotten Tomatoes Top Critics",
    ratings == "rotten_tomatoes_popcorn_meter_score" ~ "Rotten Tomatoes Popcornmeter",
    ratings == "rotten_tomatoes_popcorn_meter_verified" ~ "Rotten Tomatoes Popcornmeter (Verified)",
    ratings == "letterboxd_rating" ~ "Letterboxd Rating (Scaled)"
  ))
```


## Ratings over time

Their first plot was comparing the Pixar films' ratings over time.

```{r pixar_ratings_overview, fig.height=8, fig.width=4}
df |>
  na.omit() |>
  ggplot(aes(x = film, y = value, col = ratings)) +
  geom_point() +
  geom_line(aes(group = ratings)) +
  scale_color_brewer(palette = "Dark2") +
  labs(x = "Pixar film", y = "Rating value") +
  guides(col = guide_legend(title = "Ratings")) +
  theme_minimal() +
  scale_y_continuous(limits = c(0, 100)) +
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5),
    legend.position = "bottom",
    legend.title = element_text(size = 3),
    legend.text = element_text(size = 3)
  )
```

We can even facet the plots to see these patterns separately.

```{r pixar_ratings_overview_facet, fig.height=8, fig.width=4}
df |>
  na.omit() |>
  ggplot(aes(x = film, y = value, col = ratings)) +
  geom_point() +
  geom_line(aes(group = ratings)) +
  scale_color_brewer(palette = "Dark2") +
  labs(x = "Pixar film", y = "Rating value") +
  guides(col = guide_legend(title = "Ratings")) +
  theme_minimal() +
  scale_y_continuous(limits = c(0, 100)) +
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5),
    legend.position = "bottom",
    legend.title = element_text(size = 3),
    legend.text = element_text(size = 3)
  ) +
  facet_wrap(~ ratings, ncol = 2)
```

**Verdict**: people and critics generally agree that Cars 2 was not as good as
the other Pixar films.


## Ratings by rating group

Next, let's group the rating categories to see if there is a consistency across.

```{r pixar_ratings_group, fig.height=8, fig.width=4}
df |>
  na.omit() |>
  ggplot(aes(x = ratings, y = value, col = ratings)) +
  geom_boxplot(width = 1.75 / length(unique(df$ratings))) +
  ggbeeswarm::geom_beeswarm() +
  ggrepel::geom_label_repel(
    data = df |> na.omit() |> filter(film == "Cars 2" ),
    aes(label = film),
    point.padding = 0.5,
    nudge_x = 0.1
  ) +
  scale_color_brewer(palette = "Dark2") +
  guides(col = guide_legend(title = "Ratings")) +
  labs(x = "Rating group", y = "Rating value") +
  ylim(c(0, 100)) +
  theme_minimal() +
  theme(
    legend.position = "bottom", 
    legend.title = element_text(size = 3),
    legend.text = element_text(size = 3)
  ) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))
```

**Verdict**: people at Rotten Tomatoes generally like Pixar films more than
Metacritic and IMDb. The exception to this is Cars 2, which is consistently
lowly rated.


## Rating consistency

Are the groups statistically consistent? Let's perform
[an interclass correlation](https://en.wikipedia.org/wiki/Intraclass_correlation)
among the different critic groups.

```{r}
public_response |>
  select(
    -c(film, cinema_score, letterboxd_num_fans),
    -ends_with("counts"),
    -ends_with("votes")
  ) |>
  icc(model = "twoway", type = "consistency")
```

**Verdict**: with a null hypothesis that all critic groups are not consistent,
for the 31 Pixar films we have data for all critic groups, all groups are
consistent in rating Pixar films (p < 0.001).


## Session information

```{r}
sessionInfo()
```
