---
title: "Using pixarfilms with dm"
description: |
  Explore how to us the dm package with pixarfilms data.
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using pixarfilms with dm}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

The {pixarfilms} R package has been added to the {dm} R package, which is a
package "for working with multiple related tables, stored as data frames or in a
relational database."

Because all of the tables created in {pixarfilms} are connected by each film,
this gives an interesting opportunity to explore these interconnected tables
together.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Setup

```{r setup}
library(dm)
```


## Setup

```{r}
# Create dm object
dm <- dm(pixar_films, pixar_people, academy, box_office, genres, public_response, pixar_rankings)

# Create primary keys
dm <-
  dm %>%
  dm_add_pk(pixar_films, film) %>%
  dm_add_pk(academy, c(film, award_type)) %>%
  dm_add_pk(box_office, film) %>%
  dm_add_pk(genres, c(film, category)) %>%
  dm_add_pk(public_response, film) %>%
  dm_add_pk(pixar_rankings, c(film, source))

# Create foreign keys
dm <-
  dm %>%
  dm_add_fk(pixar_people, film, pixar_films) %>%
  dm_add_fk(academy, film, pixar_films) %>%
  dm_add_fk(box_office, film, pixar_films) %>%
  dm_add_fk(genres, film, pixar_films) %>%
  dm_add_fk(public_response, film, pixar_films) %>%
  dm_add_fk(pixar_rankings, film, pixar_films)

# Add splash of color
dm <-
  dm %>%
  dm_set_colors(
    `#5B9BD5` = pixar_films,
    `#ED7D31` = c(academy, box_office, genres, public_response),
    `#70AD47` = pixar_people
  )
```


## Explore

```{r}
dm
```

```{r}
dm %>%
  dm_examine_cardinalities()
```


```{r}
dm %>%
  dm_examine_constraints()
```


## Visualize connections

```{r}
dm_draw(dm)
```

